---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Lesson Prep

## Setup

Update Tools with "Tools -\> Update" (do not pin) - takes a long time - don't do in class

To have output go in console set in the config for the Rmd file set "chunk output in console"

To view Rmd rendered (click Knit to html) in seprate windows select settings of the Rmd file and select "Preview in Window"

Install Packages

```{r message=FALSE, warning=FALSE}
options(repos = list(CRAN="http://cran.rstudio.com/"))
install.packages(c("tidyverse", "lubridate", "ratdat"))
```

## Load

```{r}
library(tidyverse)
library(lubridate)
library(ratdat)
```

## Lessons Snippits

```{r}
install.packages("ggplot2")
```

```{r}
library(ggplot2)
library(ratdat)
?complete_old
```

```{r}
# View(complete_old)
```

```{r}
str(complete_old)
```

```{r}
ggplot(data = complete_old)
```

```{r}
ggplot(data = complete_old, mapping = aes(x = weight, y = hindfoot_length))

```

```{r}
ggplot(data = complete_old, mapping = aes(x = weight, y = hindfoot_length)) +
  geom_point()
```
## Presentatin Style

Top/bottom
```{r}
1+2
3+4
print('Hello World')

```





